---
title: "Hands_on_sessions_1_2_3"
author: "Janet Piñero (janet.pinero@upf.edu)"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"      
output:
  html_document:
    toc: true
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Pima indians diabetes dataset 
Load the Pima indians diabetes dataset (Smith et al, 1988) from the mlbench package and

Find the description of the dataset and classify the attributes according to their type

```{r}

```

What is the average age of the people in the study?

```{r}

```

How many cases and controls are there in the study? 
```{r}

```

Are there missing values in the dataset? 

```{r}

```


# 2. Worcester Heart Attack Study 
Load the dataset of from the Worcester Heart Attack Study (Saczynski et al, 2008) 

What is the average length of stay in the hospital	
```{r}

```

What is the average length of the follow up?

```{r}

```


Plot the distribution of the age by gender. Is there any trend? What is the best way to visualize this?** 
```{r}

```

# session info {.unnumbered}

```{r, results='asis',  echo=FALSE, message=FALSE }
sessionInfo()
```
